Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
stop using vref
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@705 43ef1190-90fd-4dd7-a769-d0121f02b80e

The application present users with a web interface where they can
input values for any specification they might want to search for.  In
Figure \vref{initialView} we can see how the application initially
looks for a user. Here the user can input values for the different
specifications, for instance fuel type or CO$_2$ emission. After a
user is done choosing specifications he can execute the actual car
model search. The application extracts the data from the form and
comprises it into another format that can easily be used later on. The
next step begins in the search module. Here it starts a thread for
each possible car model to execute each individual search. In the end
the user is presented with a set of valid models to choose from, which
contain the chosen specifications. In Figure \vref{afterSearch}, we
can see what the user is presented with after a successful query
execution, in this case seventeen different models. In this run, the
user have searched for a model with diesel fuel, automatic
transmission, four or more gears and a maximum of six seats. We also
have the values and URIs for each of these valid models, which means
that the application could present the user with more information than
it does today.

@@

Like the rest of the experiments we used DanielPlot to evaluate and a
package in R to visualize the result. The Figure \vref{3factorGraph}
shows the results.  Here we see no significant factors. Still there
are small effects from several factors. In Table \vref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \emph{-vso} which has an overall faster response time.

@@

In the graph \vref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. There are more than any of the previous
experiments, but it is also more factors and factor interactions.
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph. Like the six factor experiment we also see
here that there are three groups of significant factors. The first
group where most of them are placed range from around 2 seconds effect
to 11. Here there are a lot of factor interactions and why they are
there will be explained in the discussion.  The second group is very
like the second group we saw in the six factor experiment, the only
difference is that the total weight (WT) factor is substituted with
fuel consumption (FC). The last group is the same for all the
experiments, except the two factor experiment. Here we find the
ontology factor.  In Table \vref{10factorEffect} we can see the top
twenty absolute effects. This includes all the significant factors
from the last group and the second one, but also 5 from the first
group.  We can see that emission also here are present in a lot of the
entries, but so is ontology as well. The new thing here is the fuel
consumption has entered the most significant factors, and is by itself
higher than emission. The linear model again tells us that the option
\emph{-vso} has a significantly lower response time than
\emph{-co}

>>>>

The application present users with a web interface where they can
input values for any specification they might want to search for.  In
Figure \ref{initialView} we can see how the application initially
looks for a user. Here the user can input values for the different
specifications, for instance fuel type or CO$_2$ emission. After a
user is done choosing specifications he can execute the actual car
model search. The application extracts the data from the form and
comprises it into another format that can easily be used later on. The
next step begins in the search module. Here it starts a thread for
each possible car model to execute each individual search. In the end
the user is presented with a set of valid models to choose from, which
contain the chosen specifications. In Figure \ref{afterSearch}, we
can see what the user is presented with after a successful query
execution, in this case seventeen different models. In this run, the
user have searched for a model with diesel fuel, automatic
transmission, four or more gears and a maximum of six seats. We also
have the values and URIs for each of these valid models, which means
that the application could present the user with more information than
it does today.

@@

Like the rest of the experiments we used DanielPlot to evaluate and a
package in R to visualize the result. The Figure \ref{3factorGraph}
shows the results.  Here we see no significant factors. Still there
are small effects from several factors. In Table \ref{3factorEffect}
we can see the time effects from largest to smallest.  We see that the
ontology factor has the largest effect on approximately 2.2 seconds
which means that one of the ontologies overall is 2.2 seconds
faster. By reading the results from the linear model it is the factor
level \emph{-vso} which has an overall faster response time.

@@

In the graph \ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. There are more than any of the previous
experiments, but it is also more factors and factor interactions.
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph. Like the six factor experiment we also see
here that there are three groups of significant factors. The first
group where most of them are placed range from around 2 seconds effect
to 11. Here there are a lot of factor interactions and why they are
there will be explained in the discussion.  The second group is very
like the second group we saw in the six factor experiment, the only
difference is that the total weight (WT) factor is substituted with
fuel consumption (FC). The last group is the same for all the
experiments, except the two factor experiment. Here we find the
ontology factor.  In Table \ref{10factorEffect} we can see the top
twenty absolute effects. This includes all the significant factors
from the last group and the second one, but also 5 from the first
group.  We can see that emission also here are present in a lot of the
entries, but so is ontology as well. The new thing here is the fuel
consumption has entered the most significant factors, and is by itself
higher than emission. The linear model again tells us that the option
\emph{-vso} has a significantly lower response time than
\emph{-co}
